Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
Remove a bunch of marginal notes

\unsure{TODO: CCS classification; Keywords}
\section{Introduction}
\label{sec:intro}
\info{Goals of the paper: position paper: unions/intersections nice in
theory problematic in practice. In particular non-orthogonal with the
rest of the features of your language.}

@@

\section{A typology of language features}
\label{sec:feat-lang}
\info{Zoology of various features that we will eventually show
  conflict with this or that property or implementation of union and
  intersection. Including user-define contracts.}

@@

\subsection{Purity}
\label{sec:optimizations}
\info{Present inlining and CSE as two major code
optimizations.
Purity and immutability as two important factors.}

@@

\section{Union \& intersection}
\label{sec:union-inter}
\info{What are they, what are they used for.}

% Goals:
% Introduce unions and inter
% Why are they useful?
% How are they used
% How de they relate with one another

>>>>

\unsure{TODO: CCS classification; Keywords}
\section{Introduction}
\label{sec:intro}

@@

\section{A typology of language features}
\label{sec:feat-lang}

@@

\subsection{Purity}
\label{sec:optimizations}

@@

\section{Union \& intersection}
\label{sec:union-inter}
